ICM testing

### 2023-12-29 Scripts/Paper_1.Rmd
End of year update
Don't even remember what I did

```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)
loc <- 'D:/GitHub/ICM'

@@

# Doubling time, no fishing
dt.res <- NULL
n.dt.sims <- 20 # Number of simultions...
n.years <- 100
for(i in Stocks)
{
  try <- for.tunes %>% dplyr::filter(Stock == i)
  meta.tmp <- meta.sub %>% dplyr::filter(Stock == i)
  double.time <- NA
  pop <- 1000
  tmp.res <- NULL
for(s in 1:n.dt.sims)
{
  tmp <- rep(0,n.years)

@@

  ages <- 0:(ncol(fec.tmp)-1)
  n.ages <- length(ages)
  years <- tst$res$year
  n.years <- length(years)
  # Now I need to grab the fecundities and nat morts by cohort
  if(n.years > n.ages)
  {
  res.cohort <- NULL
  res.year <- NULL
  res.lambda <- NULL
  for(y in 1:(n.years-n.ages+1))
  {
    count = 0
    fs <- NA
    lx <- 1
    fs.org <- NA
    lx.org <- 1
    lx.year <- 1
    for(a in 1:n.ages)
    {
    fs[a] <- fec.tmp[y+count,a]  
    fs.org[a] <- fec.org.tmp[y+count,a]  
    if(a > 1) 
    {
      lx[a] <- lx[a-1] * m.tmp[y+count,a]  
      lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
      lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
    }  # end the a > 1 if
        count <- count + 1
    }# end the ages loop
        res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.org = lx.org,age = ages,
                               mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
                               x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
                               cohort=years[y],meta.tmp)

        res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,age = ages,
                               mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
                               x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
                               year=years[y],meta.tmp)

@@

```{r simp-figs}
theme_set(theme_few(base_size = 14))
model <- 'fec_nm'
load(file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))

pop.dam.6 <- pop.dam %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
for.tunes.6 <- for.tunes %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
res.lambda.final.6 <- res.lambda.final %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
dub.time.6 <- dub.time.summary %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
# Lambda plot

res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(LME,Area.broad) %>%
                                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))

res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(Species,Area.broad) %>%
                                             dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))

res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::group_by(Stock) %>% 
                                            dplyr::mutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T))

#hmm <- merge(tst,res.lambda.final.6,by="Stock")

# So this is lambda with fishing included
lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
                                           geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
                                           geom_hline(yintercept = 1,linetype='dashed') +
                                           facet_wrap(~G.Species,scales='free')+
                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))

@@

res.lambda.final.6$decade <- floor(res.lambda.final.6$year/10)*10

tst <- res.lambda.final.6 %>% dplyr::group_by(Stock,decade) %>% dplyr::summarise(mn.lam = mean(lam.fish,na.rm=T),
                                                                                 med.lam = median(lam.fish,na.rm=T),
                                                                                 sd.lam = sd(lam.fish,na.rm=T))
tst <- merge(tst,meta.sub,by="Stock")

tst <- tst %>% dplyr::arrange(Species,Area.broad) %>%
                                             dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))

lambda.dec.mn.plt <- ggplot(tst,aes(y=mn.lam,x=decade,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
                            geom_jitter(size=4,width = 1) +
                            scale_x_continuous(breaks=seq(1940,2020,by=10))+
                            geom_hline(yintercept = 1,linetype='dashed') +
                            facet_wrap(~G.Species,scales='free_y') +
                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
                            scale_fill_manual(name = "Stock",values = col.try)+
                            guides(colour = guide_legend(ncol = 1))+
                            theme(legend.key.width = unit(5,'cm'))
save_plot("D:/Github/ICM/Figures/tuned/lambda_decades_mean.png",lambda.dec.mn.plt,base_width = 30,base_height = 12)

lambda.dec.med.plt <- ggplot(tst,aes(y=med.lam,x=decade,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) +
                            geom_jitter(size=4,width = 1) +
                            scale_x_continuous(breaks=seq(1940,2020,by=10))+
                            geom_hline(yintercept = 1,linetype='dashed') +
                            facet_wrap(~G.Species,scales='free_y') +
                            scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
                            scale_fill_manual(name = "Stock",values = col.try)+
                            guides(colour = guide_legend(ncol = 1))+
                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm'))
save_plot("D:/Github/ICM/Figures/tuned/lambda_decades_median.png",lambda.dec.med.plt,base_width = 30,base_height = 12)

# Doubling Times
# Reorder the doubling time, either by Species and LME, or the other way around
dub.time.summary <- dub.time.summary %>%
                            dplyr::arrange(Species,LME) %>%
                            dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))

dub.heatmap.ne <- ggplot(dub.time.summary %>% dplyr::filter(LME == "NE Atlantic"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))

dub.heatmap.nw <- ggplot(dub.time.summary %>% dplyr::filter(LME == "NW Atlantic"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.22, "cm"))

dub.heatmap.pac <- ggplot(dub.time.summary %>% dplyr::filter(LME == "Pacific (Alaska)"), aes(x=year, y=Stock.short, fill= prop)) + xlab("") + ylab("")+
                            facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
                                  legend.key.width = unit(3,'cm'))

dub.heatmap <- cowplot::plot_grid(dub.heatmap.pac,dub.heatmap.nw,dub.heatmap.ne,nrow = 3,rel_heights = c(3,4,10))
dub.heatmap

save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap.png",dub.heatmap,base_width = 20,base_height = 17)

dub.time.6 <- dub.time.6 %>%
                            dplyr::arrange(LME) %>%
                            dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))

dub.heatmap.cod <- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "G. morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + 
                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))

@@

# Generation length
pop.dam <- pop.dam %>% dplyr::arrange(Species,LME) %>%
                       dplyr::mutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))

pop.dam.6 <- pop.dam.6 %>% dplyr::arrange(LME,Area.broad) %>%
                       dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))

@@

@@

# Lifetime reproductive success (no fishing)
r0.heatmap.ne <- ggplot(pop.dam %>% dplyr::filter(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
                                    xlab("") + ylab("")+
                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
                                    geom_tile() + 
                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
                                                        discrete=FALSE,trans='log') + 
                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))

@@

r0.boxplt <- ggplot(pop.dam.6) +
                            geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
                            xlab("") + scale_y_log10(name = "Lifetime Reproductive Output")+
                            facet_wrap(~G.Species,scales = 'free')+
                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
                                  axis.title.y = element_text(margin = margin(r = 30)))

@@

>>>>

```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)
library(gtable)
library(viridis)
loc <- 'D:/GitHub/ICM'

@@

# Doubling time, no fishing
dt.res <- NULL
n.dt.sims <- 2000 # Number of simulations...
n.years <- 100
for(i in Stocks)
{
  try <- for.tunes %>% dplyr::filter(Stock == i)
  meta.tmp <- meta.sub %>% dplyr::filter(Stock == i)
  double.time <- NA
  pop <- 1000
  tmp.res <- NULL
for(s in 1:n.dt.sims)
{
  tmp <- rep(0,n.years)

@@

  ages <- 0:(ncol(fec.tmp)-1)
  n.ages <- length(ages)
  years <- tst$res$year
  n.years <- length(years)
  # Now I need to grab the fecundities and nat morts by cohort
  if(n.years > n.ages)
  {
  res.cohort <- NULL
  res.year <- NULL
  res.lambda <- NULL
  for(y in 1:(n.years-n.ages+1))
  {
    count = 0
    fs <- NA
    # The lx is no fishing survivorship, zx I'm calling the survivorship including fishing
    lx <- lx.org <- lx.year <- zx <- zx.org <- zx.year <- 1
    fs.org <- NA

    for(a in 1:n.ages)
    {
    fs[a] <- fec.tmp[y+count,a]  
    fs.org[a] <- fec.org.tmp[y+count,a]  
    if(a > 1) 
    {
      # No fishing
      lx[a] <- lx[a-1] * m.tmp[y+count,a]  
      lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
      lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
      # Including fishing
      zx[a] <- zx[a-1] * z.tmp[y+count,a]  
      zx.org[a] <- zx.org[a-1]* z.org.tmp[y+count,a]  
      zx.year[a] <- zx.year[a-1] * z.tmp[y,a]
    }  # end the a > 1 if
        count <- count + 1
    }# end the ages loop
        res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.opt = lx,
                               mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
                               x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
                               zx.opt = zx,zx.opt = zx,
                               mx.zx.opt = fs*zx,mx.zx.org = fs.org*zx.org,
                               x.mx.zx.opt = fs*zx*ages,x.mx.zx.org = fs.org*zx.org*ages,
                               cohort=years[y],age = ages,meta.tmp)

        res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,
                               mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
                               x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
                               zx.opt = zx.year,
                               mx.zx.opt = unlist(fec.tmp[y,])*lx.year,
                               x.mx.zx.opt = unlist(fec.tmp[y,])*lx.year*ages,
                               age = ages,year=years[y],meta.tmp)

@@

```{r simp-figs}
theme_set(theme_few(base_size = 14))
model <- 'fec_nm'
load(file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))
pop.dam <- data.frame(pop.dam)
six.species <- c('morhua','harengus','aeglefinus','virens','solea','platessa')
pop.dam.6 <- pop.dam %>% dplyr::filter(Species %in% six.species)
for.tunes.6 <- for.tunes %>% dplyr::filter(Species %in% six.species)
dub.time.6 <- dub.time.summary %>% dplyr::filter(Species %in% six.species)
res.lambda.final$decade <- floor(res.lambda.final$year/10)*10
res.lambda.final <- res.lambda.final %>% dplyr::group_by(Stock,decade) %>% dplyr::mutate(mn.lam = mean(lam.fish,na.rm=T),
                                                                                 med.lam = median(lam.fish,na.rm=T),
                                                                                 sd.lam = sd(lam.fish,na.rm=T))
res.lambda.final <- res.lambda.final %>% dplyr::group_by(Species,decade) %>% dplyr::mutate(lm.spec.mn = mean(mn.lam,na.rm=T))              
res.lambda.final <- res.lambda.final %>% dplyr::group_by(Stock) %>% 
                                            dplyr::mutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T),
                                                          lam.no.fish.med = median(lam.no.fish,na.rm=T),
                                                          lam.fish.med = median(lam.fish,na.rm=T),
                                                          lam.org.no.fish.med = median(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.med = median(lam.org.fish,na.rm=T),) %>% data.frame()

res.lambda.final.6 <- res.lambda.final %>% dplyr::filter(Species %in% six.species)
# Sort the data into a nice order...
res.lambda.final <- res.lambda.final %>% dplyr::arrange(Species,Area.broad) %>%
                                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(Species,Area.broad) %>%
                                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
dub.time <- dub.time %>% dplyr::arrange(LME) %>%
                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))

dub.time.summary <- dub.time.summary %>% dplyr::arrange(LME,Order,Species,Area.broad) %>%
                                         dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))

dub.time.6 <- dub.time.6 %>% dplyr::arrange(LME) %>%
                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))
pop.dam <- pop.dam %>% dplyr::arrange(Species,LME) %>%
                       dplyr::mutate(Stock = forcats::fct_inorder(factor(Stock, ordered=TRUE)))
pop.dam.6 <- pop.dam.6 %>% dplyr::arrange(LME,Area.broad) %>%
                       dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))

# Lambda plots

# res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(LME,Area.broad) %>%
#                                              dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))

################### Figures in main text################### Figures in main text################### Figures in main text###################

#hmm <- merge(tst,res.lambda.final.6,by="Stock")
plot(res.lambda.final$lam.fish.med ~ res.lambda.final$lam.fish.mn)
# So this is lambda with fishing included
lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
                                           geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
                                           geom_hline(yintercept = 1,linetype='dashed') +
                                           facet_wrap(~G.Species,scales='free')+
                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))

@@

# Doubling Times

dub.heatmap.cod <- ggplot(dub.time.6 %>% dplyr::filter(G.Species == "G. morhua"), aes(x=year, y=Stock.no.species, fill= prop)) + xlab("") + ylab("")+                                     facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + 
                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + scale_x_continuous(labels=NULL) +
                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"),
                                  legend.key.width = unit(3,'cm'))

@@

# Generation length

@@

# Lifetime reproductive success (no fishing)

r0.boxplt <- ggplot(pop.dam.6) +
                            geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
                            xlab("") + scale_y_log10(name = "Lifetime Reproductive Output")+
                            geom_hline(yintercept = 1,linetype='dashed',color='blue')+
                            facet_wrap(~G.Species,scales = 'free')+
                            theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',plot.margin = margin(0,0.5,0,0.5, "cm"),
                                  axis.title.y = element_text(margin = margin(r = 30)))

################### Supplemental Figures################### Supplemental Figures################### Supplemental Figures################### Supplemental

# Reorder the doubling time, either by Species and LME, or the other way around

dub.time.summary$Order.short <- "Gadi"
dub.time.summary$Order.short[dub.time.summary$Order == "Pleuronectiformes"] <- "Plero"
dub.time.summary$Order.short[dub.time.summary$Order == "Clupeiformes"] <- "Clupei"
dub.time.summary$Order.short[dub.time.summary$Order == "Scorpaeniformes "] <- "Scor"
dub.time.summary$Order.short[dub.time.summary$Order == "Scombriformes"] <- "Scomb"
dub.time.summary$Order.short[dub.time.summary$Order == "Perciformes"] <- "Perci"

dub.time.summary <- dub.time.summary %>%
                            dplyr::arrange(G.Species,LME,Area.broad) %>%
                            dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))

dub.heatmap.gad <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Gadiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
                            xlab("") + ylab("")+                                    
                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
                            theme(legend.position = 'top',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.45, "cm"),
                                  legend.key.width = unit(3,'cm'))

dub.heatmap.pl <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Pleuronectiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
                            xlab("") + ylab("")+                                    
                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0, "cm"))

dub.heatmap.cl <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Clupeiformes"), aes(x=year, y=Stock.short, fill= prop)) + 
                            xlab("") + ylab("")+
                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,1.35, "cm"),
                                  legend.key.width = unit(3,'cm'))

dub.heatmap.per <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Perciformes"), aes(x=year, y=Stock.short, fill= prop)) + 
                            xlab("") + ylab("")+
                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2, "cm"),
                                  legend.key.width = unit(3,'cm'))

dub.heatmap.scom <- ggplot(dub.time.summary %>% dplyr::filter(Order == "Scombriformes"), aes(x=year, y=Stock.short, fill= prop)) + 
                            xlab("") + ylab("")+
                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + scale_x_continuous(labels=NULL) +
                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,2.1, "cm"),
                                  legend.key.width = unit(3,'cm'))

dub.heatmap.scorp <- ggplot(dub.time.summary %>% dplyr::filter(Order %in% "Scorpaeniformes "), aes(x=year, y=Stock.short, fill= prop)) + 
                            xlab("") + ylab("")+
                            facet_wrap(~Order.short,nrow=3,scales='free_y',strip.position = "right") + 
                            geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
                            theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.5, "cm"),
                                  legend.key.width = unit(3,'cm'))

dub.heatmap <- cowplot::plot_grid(dub.heatmap.gad,dub.heatmap.pl,dub.heatmap.cl,dub.heatmap.per,dub.heatmap.scom,dub.heatmap.scorp,
                                  nrow = 6,rel_heights = c(39,20,11,4,3,3))
dub.heatmap

save_plot("D:/Github/ICM/Figures/tuned/Doubling_time_heatmap_by_order.png",dub.heatmap,base_width = 20,base_height = 20)

lambda.dec.plt <- ggplot(res.lambda.final.6,aes(y=med.lam,x=as.factor(decade))) +
                            geom_boxplot() + scale_y_log10()+
                            xlab("Decade") + ylab("Lambda") + 
                            geom_point(aes(x=as.factor(decade),y=lm.spec.mn),color='blue',shape=8,fill='blue')+
                            #scale_x_continuous(breaks=seq(1940,2020,by=10))+
                            geom_hline(yintercept = 1,linetype='dashed') +
                            facet_wrap(~G.Species,scales='free_y') 
save_plot("D:/Github/ICM/Figures/tuned/lambda_by_decade_6.png",lambda.dec.plt,base_width = 12,base_height = 12)

@@

r0.heatmap.ne <- ggplot(pop.dam %>% dplyr::filter(LME == "NE Atlantic"), aes(x=cohort, y=Stock.short, fill= R0.opt)) + 
                                    xlab("") + ylab("")+
                                    facet_wrap(~LME,nrow=3,scales='free_y',strip.position = "right") + 
                                    geom_tile() + 
                                     scale_fill_viridis(name = "Lifetime reproductive success", breaks = c(0.4,1,2,4,10,20,40,100,200,400),
                                                        discrete=FALSE,trans='log') + 
                                    theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.9, "cm"))

@@

@@

# Doubling time for the rest of the stocks...

# dub.heatmap.no.6 <- ggplot(dub.time.summary %>% dplyr::filter(!Species %in% six.species), aes(x=year, y=Stock.short, fill= prop)) + 
#                               xlab("") + ylab("")+                                    
#                               #facet_wrap(~G.Species,nrow=3,scales='free_y',strip.position = "right") + 
#                               scale_x_continuous() +
#                               geom_tile() + scale_fill_viridis(name = "Proportion",discrete=FALSE) + 
#                               theme(legend.position = 'none',text = element_text(size=12),plot.margin = margin(0,0.5,0,0.68, "cm"))
